Canary in the Coal Mine? Civil Society Repression as a Predictor of Human Rights Abuses

### 2021-04-05 manuscript/manuscript.Rmd
Make targets for marginal effects calculations instead of the janky caching thing I had earlier

  # Load lookup list for coefficients in regression tables
  tar_load(coef_list)
})

# Temporary fake cache stuff
mfx_e1a <- readRDS(here("temp_cache", "mfx_e1a.rds"))
mfx_e1b <- readRDS(here("temp_cache", "mfx_e1b.rds"))
mfx_e1c <- readRDS(here("temp_cache", "mfx_e1c.rds"))
df_mfx_e2a <- readRDS(here("temp_cache", "df_mfx_e2a.rds"))
df_mfx_e2b <- readRDS(here("temp_cache", "df_mfx_e2b.rds"))
df_mfx_e2c <- readRDS(here("temp_cache", "df_mfx_e2c.rds"))
```

@@

```{r plot-mfx-e1a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on the probability of specific levels of political terror"}
plot_e1a_mfx <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  m_pts_total, "barriers_total", "Total legal barriers",
  m_pts_advocacy, "advocacy", "Barriers to advocacy",
  m_pts_entry, "entry", "Barriers to entry",
  m_pts_funding, "funding", "Barriers to funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

# mfx_e1a <- plot_e1a_mfx %>% 
#   mutate(fx = map2(model, plot_var, 
#                    ~conditional_effects(.x, effects = .y,
#                                         categorical = TRUE)[[1]])) %>% 
#   select(-model) %>% 
#   unnest(fx)
# saveRDS(mfx_e1a, here("temp_cache", "mfx_e1a.rds"))

mfx_e1a %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, effect2__, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = effect2__)) +
  geom_line(aes(group = effect2__), size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  position = position_dodge(width = 0.2),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_color_viridis_d(option = "plasma", end = 0.9) +
  labs(x = "Count of legal barriers\n",
       y = "Predicted probability of category",
       color = "Predicted political terror scale", fill = "Predicted political terror scale",
       title = "Political terror scale") + 
  facet_wrap(vars(plot_var_nice), scales = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

@@

```{r plot-mfx-e1b-e1c, fig.width=7.5, fig.height=5.5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on V-Dem rights indexes"}
plot_e1b_mfx <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  m_clphy_total, "barriers_total", "Total legal barriers",
  m_clphy_advocacy, "advocacy", "Advocacy",
  m_clphy_entry, "entry", "Entry",
  m_clphy_funding, "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

# mfx_e1b <- plot_e1b_mfx %>% 
#   mutate(fx = map2(model, plot_var, 
#                    ~conditional_effects(.x, effects = .y)[[1]])) %>% 
#   select(-model) %>% 
#   unnest(fx)
# saveRDS(mfx_e1b, here("temp_cache", "mfx_e1b.rds"))

plot_e1c_mfx <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  m_clpriv_total, "barriers_total", "Total legal barriers",
  m_clpriv_advocacy, "advocacy", "Advocacy",
  m_clpriv_entry, "entry", "Entry",
  m_clpriv_funding, "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

# mfx_e1c <- plot_e1c_mfx %>% 
#   mutate(fx = map2(model, plot_var, 
#                    ~conditional_effects(.x, effects = .y)[[1]])) %>% 
#   select(-model) %>% 
#   unnest(fx)
# saveRDS(mfx_e1c, here("temp_cache", "mfx_e1c.rds"))

out_mfx_e1b <- mfx_e1b %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  coord_cartesian(ylim = c(0.60, 0.71)) +
  guides(color = FALSE) +
  labs(x = NULL,
       y = "Predicted physical violence index\n(higher values = less violence)",
       title = "Physical violence index") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())

out_mfx_e1c <- mfx_e1c %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  coord_cartesian(ylim = c(0.60, 0.71)) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted civil liberties index\n(higher values = better protection)",
       title = "Private civil liberties index") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())

@@

```{r plot-mfx-e2a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on the probability of specific levels of political terror"}
# df_mfx_e2a <- conditional_effects(m_pts_v2csreprss,
#                                   effects = "v2csreprss",
#                                   categorical = TRUE)[[1]]
# saveRDS(df_mfx_e2a, here("temp_cache", "df_mfx_e2a.rds"))

out_mfx_e2a <- df_mfx_e2a %>% 
  ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, color = NA) +
  geom_line(size = 0.75) +
  scale_x_reverse() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_color_viridis_d(option = "plasma", end = 0.9) +
  scale_fill_viridis_d(option = "plasma", end = 0.9) +
  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
       y = "Predicted probability of category",
       color = "Political terror scale", fill = "Political terror scale",
       title = "Political terror scale") +
  theme_ngo()
out_mfx_e2a
```

@@

```{r plot-mfx-e2b-e2c, fig.width=7.5, fig.height=3.5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on V-Dem rights indexes"}
# df_mfx_e2b <- conditional_effects(m_clphy_v2csreprss,
#                                   effects = "v2csreprss")[[1]]
# df_mfx_e2c <- conditional_effects(m_clpriv_v2csreprss,
#                                   effects = "v2csreprss")[[1]]
# saveRDS(df_mfx_e2b, here("temp_cache", "df_mfx_e2b.rds"))
# saveRDS(df_mfx_e2c, here("temp_cache", "df_mfx_e2c.rds"))

out_mfx_e2b <- df_mfx_e2b %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#433E85", color = NA) +
  geom_line(size = 0.75, color = "#433E85") +
  scale_x_reverse() +
  coord_cartesian(ylim = c(0.5, 0.75)) +
  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
       y = "Predicted physical violence index\n(higher values = less violence)",
       title = "Physical violence index") +
  theme_ngo()

out_mfx_e2c <- df_mfx_e2c %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#4DC36B", color = NA) +
  geom_line(size = 0.75, color = "#4DC36B") +
  scale_x_reverse() +
  coord_cartesian(ylim = c(0.5, 0.75)) +
  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
       y = "Predicted civil liberties index\n(higher values = less violence)",
       title = "Private civil liberties index") +
  theme_ngo()

>>>>

  # Load lookup list for coefficients in regression tables
  tar_load(coef_list)

  # Load marginal effects
  tar_load(c(mfx_e1a_pts, mfx_e1b_clphy, mfx_e1c_clpriv,
             mfx_e2a_pts, mfx_e2b_clphy, mfx_e2c_clpriv))
})
```

@@

```{r plot-mfx-e1a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on the probability of specific levels of political terror"}
mfx_e1a_pts %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, effect2__, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = effect2__)) +
  geom_line(aes(group = effect2__), size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  position = position_dodge(width = 0.2),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_color_viridis_d(option = "plasma", end = 0.9) +
  labs(x = "Count of legal barriers\n",
       y = "Predicted probability of category",
       color = "Predicted political terror scale", fill = "Predicted political terror scale",
       title = "Political terror scale") + 
  facet_wrap(vars(plot_var_nice), scales = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

@@

```{r plot-mfx-e1b-e1c, fig.width=7.5, fig.height=5.5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on V-Dem rights indexes"}
out_mfx_e1b <- mfx_e1b_clphy %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  coord_cartesian(ylim = c(0.60, 0.71)) +
  guides(color = FALSE) +
  labs(x = NULL,
       y = "Predicted physical violence index\n(higher values = less violence)",
       title = "Physical violence index") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())

out_mfx_e1c <- mfx_e1c_clpriv %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  coord_cartesian(ylim = c(0.60, 0.71)) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted civil liberties index\n(higher values = better protection)",
       title = "Private civil liberties index") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())

@@

```{r plot-mfx-e2a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on the probability of specific levels of political terror"}
out_mfx_e2a <- mfx_e2a_pts %>% 
  ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, color = NA) +
  geom_line(size = 0.75) +
  scale_x_reverse() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_color_viridis_d(option = "plasma", end = 0.9) +
  scale_fill_viridis_d(option = "plasma", end = 0.9) +
  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
       y = "Predicted probability of category",
       color = "Political terror scale", fill = "Political terror scale",
       title = "Political terror scale") +
  theme_ngo()
out_mfx_e2a
```

@@

```{r plot-mfx-e2b-e2c, fig.width=7.5, fig.height=3.5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on V-Dem rights indexes"}
out_mfx_e2b <- mfx_e2b_clphy %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#433E85", color = NA) +
  geom_line(size = 0.75, color = "#433E85") +
  scale_x_reverse() +
  coord_cartesian(ylim = c(0.5, 0.75)) +
  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
       y = "Predicted physical violence index\n(higher values = less violence)",
       title = "Physical violence index") +
  theme_ngo()

out_mfx_e2c <- mfx_e2c_clpriv %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#4DC36B", color = NA) +
  geom_line(size = 0.75, color = "#4DC36B") +
  scale_x_reverse() +
  coord_cartesian(ylim = c(0.5, 0.75)) +
  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
       y = "Predicted civil liberties index\n(higher values = less violence)",
       title = "Private civil liberties index") +
  theme_ngo()
